---
title: "Changing trends in the prevalence of _H. pylori_ infection in Japan (1908-2003): a systematic review and meta-regression analysis of 170,000 individuals"
author: Chaochen Wang^1^, Takeshi Nishiyama^1^, Shogo Kikuchi^1^, Manami Inoue^2^,  Norie Sawada^2^, Shoichiro Tsugane^2^, Yingsong Lin^1^
email: "abelardccwang@gmail.com"
institute: | 
    | 1 Department of Public Health, Aichi Medical University, Nagakute, Aichi, Japan; 
    | 2 Epidemiology and Prevention Group, Center for Public Health Sciences, National Cancer Center, Tokyo, Japan
longinstitute: "Aichi Medical University"
web: "winterwang.github.io"
logo: "images/lg.png"
#backimg: "images/logo.png"
bibliofiles: "bib/bib.bib"
posteroptions: width=90,height=140,scale=1.2 #,grid # portrait
#posteroptions: width=110,height=90,scale=1.2 #,grid # landscape
headerheight: 18cm
colorstyle:
# large, Large, LARGE, huge, Huge, veryHuge, VeryHuge, VERYHuge
titlefont: size=\huge,series=\bfseries
authorfont: size=\LARGE
institutefont: size=\LARGE
knit: (function(input, encoding, make = TRUE) { source('tex/makefile-renderer.R', local = TRUE) })
---

%% smart
%% to=latex
%% template=tex/poster_ocean.tex
%% filter=tex/poster-filters.py
%% biblatex

```{r packages-and-options, cache=FALSE}
library('ggplot2')
library('knitr')
theme_set(theme_grey(base_size=10))
knitr::opts_chunk$set(fig.width = 16, fig.height = 4)
```

[columns=2]

[column]

# BACKGROUND

-  Gastric cancer burden remains high in Japan, where it is the second-leading cause of cancer deaths, accounting for annual deaths of approximately 50,000 in Japan.

-  Substantial evidence supports a central role for _H. pylori_ in the parthenogenesis of upper-gastrointestinal diseases, including peptic ulcer and noncardia gastric cancer.

-  Cross-sectional studies have suggested that the prevalence of _H. pylori_ infection increases with age, while the whole picture remains obscure.

-  We systematically reviewed the existing literature that presented estimates of the prevalence of _H. pylori_ infection in the Japanese population.

-  The obejectives are: (1) to derive a robust prevalence estimate of _H. pylori_ infection by birth year; (2) to clarify whether _H. pylori_ infection exhibits a birth-cohort pattern. 

<!--

- Standard abreviations \\eg and \\ie for \eg and \ie
- Units like \pps{900}
- **Highlights** and *highlights*

-->

# METHODS

Before starting, you have to install R, RStudio, bookdown package, and other software and packages (\ie `Pandoc`, \LaTeX, `rmarkdown`, `rticle`, `knitr`, etc.) which bookdown depends on. See the official manual of [bookdown](https://bookdown.org/yihui/bookdown/) for details.

Installation:

`devtools::install_github("pzhaonet/bookdownplus")`

Run the following codes, and you will get some files (e.g. index.Rmd and body.Rmd) and folders in your working directory.

`bookdownplus::bookdownplus()`

Now press `ctrl+shift+b` to compile it. Your will get a book file named `index.pdf` in `_book/`  folder.

Write your own text in `index.Rmd` and `body.Rmd`, and build your own lovely book. Have fun!


# Graphs

Using `bookdown` or `rmarkdown`, users can insert figures into a document in a friendly way. Just embed the R scripts into your `.Rmd` file(s) and compile it/them with knitr package, and the figures will appear automatically with high resolution and reproductivity.

<!--

```{r co2, cache = TRUE, echo = FALSE, fig.cap='Carbon dioxide concentration, observed at Mauna Loa.'}
plot(co2)
```

-->

```{r iris, cache=TRUE, echo=FALSE, fig.cap='IRIS data plotted with R ggplot2 package.'}
ggplot(iris, aes(Sepal.Length, Petal.Length)) +
    geom_point(aes(color = Species)) +
    facet_wrap(~ Species)
```

<!-- Comments -->


# Table

Similarly to graphs, tables can be inserted either with R script or with markdown syntax.

<!--

header x  header y
--------- ----------
x1        y1
x2        y2

-->

```{r tab1, tidy=FALSE, echo=FALSE}
knitr::kable(
  head(iris, 3), caption = 'IRIS data as an example.',
  booktabs = TRUE
)
```

# Bibliography

\printbibliography


[column]

# Book types supported by `bookdownplus`

Some sample pages are displayed as follows. More details can be found in the tutorial book [@R-bdp].


\begin{figure}[htp]
  \includegraphics[width=.33\textwidth]{images/mail.pdf}\hfill
  \includegraphics[width=.33\textwidth]{images/mail.pdf}\hfill
  \includegraphics[width=.33\textwidth]{images/mail.pdf}
\end{figure}    

\begin{figure}[htp]
  \includegraphics[width=.33\textwidth]{images/mail.pdf}\hfill
  \includegraphics[width=.33\textwidth]{images/mail.pdf}\hfill
  \includegraphics[width=.33\textwidth]{images/mail.pdf}
\end{figure}    

\begin{figure}[htp]
  \includegraphics[width=.33\textwidth]{images/mail.pdf}\hfill
  \includegraphics[width=.33\textwidth]{images/mail.pdf}\hfill
  \includegraphics[width=.33\textwidth]{images/mail.pdf}
\end{figure}    


# Take-home message

- `R bookdownplus` is an extension of `bookdown` for academic and literal writing, especially for reproducible reports.

- `R bookdownplus` is still being developed. Feel free to join me either in contributing templates to [**my Github repo**](https://github.com/pzhaonet/bookdownplus) ^[https://github.com/pzhaonet/bookdownplus], or in writing the tutorial of R bookdownplus [@R-bdp].

<!--\vskip0.5cm

[/columns]


[columns=2]

[column]

-->

# Acknowledgements

Many thanks to Dr. Yihui Xie for his amazing generosity and incredible patience in helping me get into the wonderful world of R bookdown.

The open source codes from Github and R community are much appreciated.

\vskip1.5cm


<!--\vskip4.4cm-->

[/columns]
